Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-05 paper.qmd
rolling draft saved again

### Motus R Package
<p><em>Birds Canada</em>, the creator of the radio telemetry network of <em>Motus</em>, has detailed documentation for an R package to use the <em>Motus</em> data. The website for this package gives extensive instruction on how to get started using the <em>Motus</em> database in R, how to access data, how to make sense of tag and receiver deployments, how to clean the data, and examples of how to explore the data. </p>

@@

<p>There are two types of detection databases that a user can access. One is a receiver database, comprised of every detection of registered tags at one receiver The second is a project database, comprised of every detection of specific or your registered tags across the entire <em>Motus</em> network. The latter was used for this project. </p>

@@

### Data Cleaning
- initial cleaning
- getting to species
- getting unique bird IDs

### Exploration of Data
- initial plots and exploration

>>>>

### Motus R Package

<p><em>Birds Canada</em>, the creator of the radio telemetry network of <em>Motus</em>, has detailed documentation for an R package to use the <em>Motus</em> data. The website for this package gives extensive instruction on how to get started using the <em>Motus</em> database in R, how to access data, how to make sense of tag and receiver deployments, how to clean the data, and examples of how to explore the data.</p>

@@

<p>There are two types of detection databases that a user can access. One is a receiver database, comprised of every detection of registered tags at one receiver The second is a project database, comprised of every detection of specific or your registered tags across the entire <em>Motus</em> network. The latter was used for this project.</p>

@@

### Data Cleaning

-   initial cleaning
-   getting to species
-   getting unique bird IDs

### Exploration of Data

-   initial plots and exploration
